---
title: "Final Project Submission"
author: "Moldatayeva Assem"
date: "17/04/2024"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
The objective of this task is to develop a product showcasing the prediction algorithm you've constructed and to offer an accessible interface for users. Your submission should include:<br>

A Shiny application that accepts a phrase input (comprising multiple words) in a text box and generates a prediction for the next word.<br>
A presentation deck with a maximum of five slides, crafted using R Studio Presenter, designed to pitch your algorithm and app as if addressing your boss or an investor.<br>



## Algorithm used to make prediction
```{r,echo=TRUE}
predictWord <- function(the_word) {
    word_add <- stripWhitespace(removeNumbers(removePunctuation(tolower(the_word),preserve_intra_word_dashes = TRUE)))
    # testing print("word_add")
    the_word <- strsplit(word_add, " ")[[1]]
    # testing print("the_word")
    n <- length(the_word)
    # testing print(n)
    
    ########### check Bigram
    if (n == 1) {the_word <- as.character(tail(the_word,1)); functionBigram(the_word)}
    
    ################ check trigram
    else if (n == 2) {the_word <- as.character(tail(the_word,2)); functionTrigram(the_word)}
    
    ############### check quadgram
    else if (n >= 3) {the_word <- as.character(tail(the_word,3)); functionQuadgram(the_word)}
}
```



## Functioning of the App

1. The first task  is to load the libraries.
2. Next we load the bigram, trigram and quadgram frequencies words matrix frequencies
3. Next we use the function to predict the word.
4. Then we use the function predictWord



## Experience using the app

1. The app uses the correct prediction algorithm for words prediction
2. The results shown uses the functions for prediction.

##The link for GITHUB and RPub

Below are the link for github 

https://github.com/abhijeetkmohite/Peer-graded-Assignment-Final-Project-Submission

Below is the link for Rpub

https://rpubs.com/abhijeetkmohite/data_science_capstone

## Thank You

Thank you all for viewing my presentation

